$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-29 paper/e6ssm-tuning-paper.tex
Completed sentence that had end missing (I think the completion is correct, the relic density is accounted for by the ordinary neutralino?)

There are still several remaining options. One may specialize to
scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
singlinos that cause these problems are entirely decoupled and the
relic abundance is fitted with a bino-like candidate with a novel
mechanism involving back-scattering into a heavier inert
Higgsino. Another well motivated scenario admits two possible dark
matter candidates \cite{Nevzorov:2012hs}, where one will be an inert
singlino and the other will have a similar composition to MSSM
neutralinos. The simplest phenomenologically viable solution in that
case is to make the singlinos extremely light hot dark matter
candidates and explains almost all the relic abundance density with
\textbf{[***How does this sentence end? Or is the with not meant to be there?***]}

@@

>>>>

There are still several remaining options. One may specialize to
scenarios known as the EZSSM \cite{Hall:2011zq} where the inert
singlinos that cause these problems are entirely decoupled and the
relic abundance is fitted with a bino-like candidate with a novel
mechanism involving back-scattering into a heavier inert
Higgsino. Another well motivated scenario admits two possible dark
matter candidates \cite{Nevzorov:2012hs}, where one will be an inert
singlino and the other will have a similar composition to MSSM
neutralinos. The simplest phenomenologically viable solution in that
case is to make the singlinos extremely light hot dark matter
candidates and accounts for almost all the relic abundance density with
the lightest ordinary neutralino.

@@

\bibliographystyle{apsrev4-1}
